Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-08-20 awipev-CO2.Rmd
adding RMSE on property plots

#################### Function RMSE root mean square error
rmse <- function(error) { sqrt(mean(error^2)) }
#rmse(fit$residuals)

@@

fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu_ctd_9m , nperm = 99)

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu_ctd_9m , nperm = 99)
p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(month))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") +theme_bw()

@@

## pHs 
Comparaison is done here with **corrected pHs** (**seaFET**, **durafet** and **calculated** (from AT/CT)) and normalized at 4°C with a total alkalinity of 2273 µmoles kg-1 (mean data). For information, mean temperatures in Ferrybox and *in situ* are repectively 3.5°C and 2.5°C.

@@

pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

pH_dur <- d_all %>%
  dplyr::select(datetime, sal_fb,temp_fb, ph_dur_corr)%>%
  dplyr::filter(!is.na(ph_dur_corr), !is.na(temp_fb), !is.na(sal_fb))
pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

# join pH sf norm + pH dur norm
d_all <- left_join(d_all, pH_sf%>%dplyr::select(datetime,pHint_tot_sf_norm4 ), by="datetime")
d_all <- left_join(d_all, pH_dur%>%dplyr::select(datetime,pH_durafet_norm4 ), by="datetime")

>>>>

#################### Function RMSE for model 2 regression root mean square error
lm2 <- function(x, y) { 
  fit <- lmodel2(y  ~ x , nperm = 99)
  intercept <- fit$regression.results[2,2]
  slope <- fit$regression.results[2,3]
  predicted <- intercept + x * slope
  error <- predicted - x
  my_list <- list(fit = fit, rmse = sqrt(mean(error^2, na.rm=TRUE)))
  return(my_list)
  }

@@

lm2 <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(month))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = lm2$fit$regression.results[2,2], slope = lm2$fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(lm2$fit$rsquare, 3),
                     "; Intercept =", signif(lm2$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm2$fit$regression.results[2,3], 3),
                     "; P =", signif(lm2$fit$P.param, 3),
                     "; RMSE = ", signif(lm2$rmse, 3))) +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()

@@

## pHs 
Comparaison is done here with **corrected pHs** (**seaFET**, **durafet** and **calculated** (from AT/CT)) and normalized at 4°C with a total alkalinity of `r mean(d_all$at, na.rm=TRUE)` µmoles kg-1 (mean data). For information, mean temperatures in Ferrybox and *in situ* are repectively 3.5°C and 2.5°C.

@@

pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

pH_dur <- d_all %>%
  dplyr::select(datetime, sal_fb,temp_fb, ph_dur_corr)%>%
  dplyr::filter(!is.na(ph_dur_corr), !is.na(temp_fb), !is.na(sal_fb))
pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

# join pH sf norm + pH dur norm
d_all <- left_join(d_all, pH_sf%>%dplyr::select(datetime, pHint_tot_sf_norm4 ), by="datetime")
d_all <- left_join(d_all, pH_dur%>%dplyr::select(datetime, pH_durafet_norm4 ), by="datetime")
